---
title: "Exercises 1. Vectors"
author: "Tiffany Cheng"
output: pdf_document
---

## 1. Create the vectors:
### (a) (1, 2, 3, . . . , 19, 20)
```{r} 
1:20
```

### (b) (20, 19, . . . , 2, 1)
```{r}
20:1
```

### (c) (1, 2, 3, . . . , 19, 20, 19, 18, . . . , 2, 1)
```{r}
c(1:20,19:1)
```

### (d) (4, 6, 3) and assign it to the name tmp
```{r}
tmp <- c(4, 6, 3)
tmp
```

### (e) (4, 6, 3, 4, 6, 3, . . . , 4, 6, 3)
```{r}
rep(tmp,10)
```

### (f) (4, 6, 3, 4, 6, 3, . . . , 4, 6, 3, 4)
```{r}
rep(tmp,len=31)
```

### (g) (4, 4, . . . , 4, 6, 6, . . . , 6, 3, 3, . . . , 3)
```{r}
rep(tmp,times=c(10,20,30))
```

## 2. Create a vector of the values of 
$e^x cos(x)$ at x = 3, 3.1, 3.2, . . . ,6.
```{r}
values <- seq(3,6,by=0.1)
exp(values)*cos(values)
```

## 3. Create the following vectors:
### (a)
$(0.1^3 0.1^1, 0.1^6 0.2^4, ... ,0.1^{36} 0.2{34})$
```{r}
first <- seq(3,36,by=3)
second <- seq(1,34,by=3)
(0.1^first)*(0.2^second)
```

### (b)
$(2, \frac{2^2}{2}, \frac{2^3}{3}, ... ,\frac{2^{25}}{25})$
```{r}
(2^(1:25))/(1:25)
```

##  4. Calculate the following:
### (a)
$\sum_{i = 10}^{100}(i^3 + 4i^2)$
```{r}
i <- 10:100
sum(i^3+4*i^2)
```

### (b)
$\sum_{i=1}^{25}(\frac{2^i}{i}+\frac{3^i}{i^2})$
```{r}
i <- 1:25
sum((2^i)/i+(3^i)/i^2)
```

## 5. Use the function paste to create the following character vectors of length 30:
### (a) ("label 1", "label 2", ....., "label 30")
```{r}
paste("label",1:30)
```

### (b) ("fn1", "fn2", ..., "fn30")
```{r}
paste("fn",1:30,sep="")
```

## 6. Execute the following lines which create two vectors of random integers which are chosen with replacement from the integers 0, 1, . . . , 999. Both vectors have length 250.
```{r}
set.seed(50)
xVec <- sample(0:999, 250, replace=T)
yVec <- sample(0:999, 250, replace=T)
```
Suppose $x = (x_1, x_2, . . . ,x_n)$ denotes the vector xVec and $y = (y_1, y_2, . .  ,y_n)$ denotes the vector yVec.
### (a) Create the vector
$(y_2 - x_1, . . . , y_n - x_{n-1})$.
```{r}
yVec[-1]-xVec[-length(xVec)]
```

### (b) Create the vector
$(\frac{sin(y_1)}{cos(x_2)}, \frac{sin(y_2)}{x_3}, ...,\frac{y_{n-1}}{cos(x_n)})$.
```{r}
sin(yVec[-length(yVec)])/cos(xVec[-1])
```

### (c) Create the vector
$(x_1 + 2x_2 - x_3, x_2 + 2x_3 - x_4, ..., x_{x-2} + 2x_{n-1} - x_n)$
```{r}
xVec[-c(249,250)]+2*xVec[-c(1,250)]-xVec[-c(1,2)]
```

### (d) Calculate
$\sum\limits_{i=1}^{n-1} \frac{e^{-x_{i+1}}}{x_i + 10}$
```{r}
sum(exp(-xVec[-1])/(xVec[-length(xVec)]+10))
```

## 7. This question uses the vectors xVec and yVec created in the previous question and the functions sort, order, mean, sqrt, sum and abs.
### (a) Pick out the values in yVec which are > 600.
```{r}
yVec[yVec>600]
```

### (b) What are the index positions in yVec of the values which are > 600?
```{r}
which(yVec>600)
```

### (c) What are the values in xVec which correspond to the values in yVec which are > 600? (By correspond, we mean at the same index positions.)
```{r}
xVec[yVec>600]
```

### (d) Create the vector 
$(|x_1 - \bar{x}|^{1/2}, |x_2 - \bar{x}|^{1/2}, ..., |x_n - \bar{x}|^{1/2})$ where x-bar denotes the mean of the vector x = (x1, x2, . . . , xn).
```{r}
sqrt(abs(xVec-mean(xVec)))
```

### (e) How many values in yVec are within 200 of the maximum value of the terms in yVec?
```{r}
sum(yVec>max(yVec)-200)
```

### (f) How many numbers in xVec are divisible by 2? (Note that the modulo operator is denoted %%.)
```{r}
sum(xVec%%2==0)
```

### (g) Sort the numbers in the vector xVec in the order of increasing values in yVec.
```{r}
xVec[sort.list(yVec)]
```

### (h) Pick out the elements in yVec at index positions 1, 4, 7, 10, 13, . . . .
```{r}
yVec[seq(1,250,by=3)]
```

## 8. By using the function cumprod or otherwise, calculate
$1 + \frac{2}{3} + (\frac{2}{3}\frac{4}{5}) + (\frac{2}{3}\frac{4}{5}\frac{6}{7} + ... + (\frac{2}{3}\frac{4}{5} ... \frac{38}{39}))$
```{r}
1+sum(cumprod(seq(2,38,by=2)/seq(3,39,by=2)))
```